A Parallel, Backjumping Subgraph Isomorphism Algorithm using Supplemental Graphs

### 2015-08-23 talk/talk.tex
A few tweaks

\usepackage{tikz}
\usepackage{xcolor}
\usepackage{complexity}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{amsmath}                   % \operatorname
\usepackage{amsfonts}                  % \mathcal
\usepackage{amssymb}                   % \nexists
\usepackage{gnuplot-lua-tikz}          % graphs
\usepackage[vlined]{algorithm2e} % algorithms

@@

\begin{frame}{The Basic CP Model}
    \begin{itemize}
        \item One variable for each vertex in the pattern graph, with the domains being the vertices
            of the target graph.
        \item If two vertices are adjacent in the pattern, their values must be adjacent
            in the target.
            \begin{itemize}
                \item In the \emph{induced} variant, non-adjacent vertices must be mapped to
                    non-adjacent vertices. We only discuss the non-induced variant in this talk.
            \end{itemize}
        \item All pattern vertices must be given different values.
        \item Often enhanced: for example, we can filter based upon degree.
    \end{itemize}
\end{frame}

\begin{frame}{Another Perspective}
    \begin{itemize}
        \item The variables describe an injective mapping from the pattern to the target, which
            preserves adjacency.
    \end{itemize}
\end{frame}

\begin{frame}{Selected Previous Work}
    \begin{itemize}
        \item VF2: backtracking search, interesting heuristics. Widely used. \\[0.1cm]
            {\scriptsize A (Sub)Graph Isomorphism Algorithm for Matching Large Graphs. Luigi P.
            Cordella and Pasquale Foggia and Carlo Sansone and Mario Vento. {IEEE} Trans.
        Pattern Anal. Mach. Intell., 2004.}

        \item LAD: locally all-different, and neighbourhood degree sequences. \\[0.1cm]
            {\scriptsize AllDifferent-based filtering for subgraph isomorphism. Christine Solnon.
            Artif. Intell., 2010.}
        \item SND: distance-based filtering. \\[0.1cm]
            {\scriptsize Scoring-Based Neighborhood Dominance for the Subgraph Isomorphism Problem.
            Gilles Audemard and Christophe Lecoutre and Mouny Samy Modeliar and Gilles
        Goncalves and Daniel Porumbel. CP 2014.}
    \end{itemize}
\end{frame}

@@

            \node [anchor=center, font=\huge] at (2.565, 0.5) { $\not\hookrightarrow$ };

@@

            \item For any $d$, a subgraph isomorphism $i : P \hookrightarrow T$ is also a
                subgraph isomorphism $i^d : P^d \hookrightarrow T^d$.
        \end{itemize}

@@

\begin{frame}{Counting-Based All-Different}
    \begin{itemize}
        \item \emph{If it looks like I'll have lots of time: explain and animate this}
    \end{itemize}
\end{frame}

\begin{frame}{Backjumping}
    \begin{itemize}
        \item Rather than backtracking on failure, we can sometimes show it's safe to jump back
            several levels immediately.
        \item This can be done with without explicit conflict sets, and without modifying
            propagators.
        \item See the paper for details.
    \end{itemize}
\end{frame}

@@

\begin{frame}{Sidenote on Safety, Parallelism, and Benchmarking}
    \begin{itemize}
        \item We guarantee:
            \begin{itemize}
                \item Parallel search will never be substantially worse than sequential search.
                \item Adding more cores will never make things substantially worse (excluding
                    hardware weirdness).
                \item Running it twice will give more or less the same runtimes.
            \end{itemize}
        \item All comparisons are against a dedicated sequential implementation of a strong
            algorithm, not a threaded implementation run with one thread.
    \end{itemize}
\end{frame}

>>>>

\usepackage{tikz}
\usepackage{xcolor}
\usepackage{complexity}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{amsmath}                   % \operatorname
\usepackage{amsfonts}                  % \mathcal
\usepackage{amssymb}                   % \nexists
\usepackage{gnuplot-lua-tikz}          % graphs
\usepackage[vlined]{algorithm2e} % algorithms
\usepackage{centernot}

@@

\begin{frame}{The Basic CP Model}
    \begin{itemize}
        \item One variable for each vertex in the pattern graph, with the domains being the vertices
            of the target graph.
        \item If two vertices are adjacent in the pattern, their values must be adjacent
            in the target.
            \begin{itemize}
                \item In the \emph{induced} variant, non-adjacent vertices must be mapped to
                    non-adjacent vertices. We only discuss the non-induced variant in this talk.
            \end{itemize}
        \item All pattern vertices must be given different values.
        \item Often enhanced: for example, we can filter based upon degree.
        \item Another perspective: the variables describe an injective mapping from the pattern to
            the target, which preserves adjacency.
    \end{itemize}
\end{frame}

\begin{frame}{Selected Previous Work}
    \begin{itemize}
        \item VF2: backtracking search, interesting heuristics. Widely used. \\[0.1cm]
            {\scriptsize A (Sub)Graph Isomorphism Algorithm for Matching Large Graphs. \emph{Luigi P.
                Cordella, Pasquale Foggia, Carlo Sansone and Mario Vento}. {IEEE} Trans.
        Pattern Anal. Mach. Intell., 2004.}

        \item LAD: locally all-different, and neighbourhood degree sequences. \\[0.1cm]
            {\scriptsize AllDifferent-based filtering for subgraph isomorphism. \emph{Christine
                Solnon}.  Artif. Intell., 2010.}
        \item SND: distance-based filtering. \\[0.1cm]
            {\scriptsize Scoring-Based Neighborhood Dominance for the Subgraph Isomorphism Problem.
                \emph{Gilles Audemard, Christophe Lecoutre, Mouny Samy Modeliar, Gilles
            Goncalves and Daniel Porumbel}. CP 2014.}
    \end{itemize}
\end{frame}

@@

            \node [anchor=center, font=\huge] at (2.565, 0.5) { $\centernot\rightarrowtail$ };

@@

            \item For any $d$, a subgraph isomorphism $i : P \rightarrowtail T$ is also a
                subgraph isomorphism $i^d : P^d \rightarrowtail T^d$.
        \end{itemize}

@@

\begin{frame}{Counting-Based All-Different}
    \begin{itemize}
        \item One pass through the variables, from smallest domain to largest.

        \item Track unions of domains as we go along.

        \item Eliminate any detected Hall sets from future variables.

        \item This can miss some deletions, but has a very fast bitset implementation for large
            domains.
    \end{itemize}
\end{frame}

\begin{frame}{Backjumping}
    \begin{itemize}
        \item Rather than backtracking on failure, we can sometimes show it's safe to jump back
            several levels immediately.
        \item This can be done with without explicit conflict sets, and without modifying
            propagators.
        \item Producing smaller conflict sets from a failed all-different gives better results.
    \end{itemize}
\end{frame}

@@

\begin{frame}{Sidenote on Safety, Parallelism, and Benchmarking}
    \begin{itemize}
        \item The way we do parallelism guarantees:
            \begin{itemize}
                \item Parallel search will never be substantially worse than sequential search.
                \item Adding more cores will never make things substantially worse (excluding
                    hardware weirdness).
                \item Running it twice will give more or less the same runtimes.
            \end{itemize}
        \item All comparisons are against a dedicated sequential implementation of a strong
            algorithm, not a threaded implementation run with one thread.
    \end{itemize}
\end{frame}
